SPARQL on the open, decentralised Web

### 2016-06-02 dissertation/motivation.tex
caching section

However, we note that the Internet infrastructure is accommodating for
solving parts of this problem with the presence of caches at several
different levels. Some clients also have significant processing
capacity, and these are among the factors that could make SPARQL query
answering on the open Web practically feasible. The focus of this work
is to ease the burden of servers by allowing other parties to take
parts of the query evaluation.

@@

\subsection{Philosophy of Science}

@@

>>>>

@@

\subsection{Philosophy of Science and statistical methods}

@@

I became early quite confident that the practice of benchmarking was
an easy target, with its lack of summary statistics and inability to
support proper hypothesis testing, standardising to deal with
complexity rather than methodological advances, and lack of ability to
formulate the experiment as severe enough.

\subsection{Caching in the Internet}

Clearly, the above motivation points out federated SPARQL as a key
solution to the problem of query answering over decentralised sources,
and that was originally where I intended my main contributions. During
the work, it became clear that the stability of individual endpoints
would need to addressed first. In the detailed problem descriptions,
this will be further discussed, the choice of caching is the main
focus is somewhat arbitrary.

It is crucial, however, that we note that the Internet infrastructure
is accommodating for solving parts of this problem with the presence
of caches at several different levels. We would need to create an
infrastructure to take advantage of these caches, and encourage data
publishers to include metadata to allow caches to be managed in a
standard-defined way. The scale at which this can already be done was
at first important to understand.

We further note that some clients also have significant processing
capacity and could process SPARQL queries themselves. Others, like
microcontrollers on the Internet of Things, cannot. This calls for a
diverse infrastructure that can accommodate all kinds of
clients. Nevertheless, these are among the factors that
could make SPARQL query answering on the open Web practically
feasible.

The convergence of all the directions of this work was intended to be
a contribution to ease the burden of servers by allowing other parties
to take parts of the query evaluation.
